Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 README.Rmd
returned to the png
working on updating and moving sumbission to do list to an R script

```{r echo = FALSE}
unzip("figure-static/figure-readme.png.zip")
knitr::include_graphics("figure-static/figure-readme.png")
```

@@

- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
- `file-organization.R` contains R code for organizing the files to be added to the GitHub repository and preparing and moving files to the submission folder.
- `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.

>>>>

```{r echo = FALSE}
knitr::include_graphics("figure-static/figure-readme.png")
```

@@

- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
- `figure-compression.R` contains R code for compressing the static figure used in the manuscript
- `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
